Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-10 WSSSPE2_report/WSSSPE2_review.tex
Alphabetized names and removed duplicates
Also removed trailing commas. Added my name to contributors.

\author{TBD by contributions}
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$}
%
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}

@@

\todo{VOLUNTEER NEEDED to neaten this - alphabetize, columnize, add short intro sentence that these were generated from people who signed the google doc saying they were there and are not complete, also added names from breakout groups}

Daniel S. Katz, U Chicago \& Argonne
Gabrielle Allen, U Illinois
Alice Allen, Astrophysics Source Code Library (ASCL)
Neil Chue Hong, Software Sustainability Institute \& University of Edinburgh, N 
Tom Crick, Cardiff Metropolitan University, UK
Samin Ishtiaq, Microsoft Research Cambridge, UK
Matt Turk, NCSA/UIUC
Colin C. Venters, University of Huddersfield
Wolfgang Bangerth
Carl Boettiger, UCSC/ropensci,
Chris Bogart, ISR/CMU
Abani Patra, Univ @ Buffalo
Kyle Marcus, Univ @ Buffalo
Karen Cranston, NESCent
Andre Luckow, Rutgers
Marlon Pierce, Indiana University, 
Frank L\"{o}ffler, Louisiana State University,
Steven R. Brandt, Louisiana State University, 
James Howison, University of Texas
Ray Idaszak, RENCI/UNC,
Chris Lenhardt, 
Robert H. McDonald - Indiana University - Data to Insight Center/Libraries - 
Marcus D. Hanwell, Kitware, 
Tom Clune - NASA GSFC - 
Mike Rilee - NASA/GSFC, Rilee Systems Technologies - 
Sarah Harris, University of Leeds, 
James Spencer, Imperial College London,
John W. Peterson, Idaho National Laboratory,
Cody J Permann, Idaho National Laboratory, 
Richard Littauer, MIT/University of Saarland 
Aleksandra Pawlik, Software Sustainability Institute, 
Jordan Adams, Tulane University, 
Jory Schossau, Michigan State University, 
Robert R Downs, CIESIN, Columbia University, 
Ethan Davis, UCAR Unidata, 
Nancy Wilkins-Diehr, SDSC, 
Suresh Marru, Indiana University 
Hilmar Lapp, National Evolutionary Synthesis Center (NESCent) and Duke University, 
Bryan Marker, The University of Texas at Austin,  
James Shepherd, Rice University, 
Ethan White, University of Florida/Utah State University, 
Mark Schildhauer,  NCEAS, Univ. Calif, Santa Barbara
Carol Song, Purdue University, 
John W. Cobb, 
Matt Jones,  University of California Santa Barbara
Erin Robinson, Foundation for Earth Science 
Nick Jones, New Zealand eScience Infrastructure, University of Auckland, 
Yolanda Gil, Information Sciences Institute, University of Southern California, 
Karthik Ram, , University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
Sushil Prasad, Georgia State University, Atlanta 
Nicole Gasparini, Tulane University, New Orleans
Stephen Piccolo,  Brigham Young University, Utah
David Henty,  EPCC, The University of Edinburgh
Alan Simpson,  EPCC, The University of Edinburgh
Berkin Malkoc, Istanbul Technical University
Pierre-Yves Aquilanti TOTAL E\&P R\&T USA
Greg Wilson  Software Carpentry
Anshu Dubey  Lawrence Berkeley National Laboratory
Sol Greenspan  National Science Foundation
Tracy Teal Data Carpentry
Frank Seinstra Netherlands eScience Center
Dirk Colbry, Michigan State University
Kaitlin Thaney,  Mozilla Science Lab, 
Ted Habermann, The HDF Group
Benjamin Pharr, University of Mississippi, 
Eric Hutton,  University of Colorado
Ray Plante, NCSA/University of Illinois Urbana-Champaign
Kurt Glaesemann Pacific northwest national lab
Ardita Shkurti University of Nottingham
Andy Nutter-Upham, Whitehead Institute,
David Bernholdt, Oak Ridge National Laboratory

Names below are from working groups - probably duplicates of above but perhaps not all...

Colin C. Venters, University of Huddersfield
Erin Robinson, Foundation for Earth Science, 
Robert Downs, CIESIN 
Justin Shi
Ethan Davis 
Kyle Marcus
Andy Nutter-Upham, Whitehead Institute, 
Abani Patra

Chris Lenhardt , Nancy Wilkins-Diehr , Marcus Hanwell , Tracy Teal , Jory Schossau , Andre Luckow

Ian Kelley 
Ray Idaszak 
Ray Plante 
Anshu Dubey
Dirk Colbry 
Dan Katz
Chris Bogart
Sol Greenspan

Kaitlin Thaney
Abani Patri
Frank Seinstra
Frank Loffler
Richard
Robert McDonald
Steven Brandt

Samin Ishtaq, Nathan Weeks, Rupert Nash, Stephen Piccolo, Hilmar Lapp, Tom Crick, Jakob Blomer, Neil Chue Hong

Sarah Harris, Carl Boettiger, Bryan Marker, Berkin Malkoc, Carol Song, Mark Schildhauer, Benjamin Pharr

Karen Cranston, National Evolutionary Synthesis Center,
Greg Wilson, Software Carpentry, 
Wolfgang Bangerth 
Ethan White, Utah State Univ/University of Florida, 
John Peterson, Idaho National Laboratory, jwpeterson@gmail.com, 
David Bernholdt
Aleksandra Pawlik, Software Sustainability Institute, 
Kurt Glaesemann
Cody Permann
Maxime Hughes
Anshu Dubey
Tom Clune
Mike Rilee

>>>>

\author{TBD by contributions}
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,}
%Richard Littauer$^{(9)}$ \\
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%

@@

\todo{VOLUNTEER NEEDED to neaten this - columnize, add short intro sentence that these were generated from people who signed the google doc saying they were there and are not complete, also added names from breakout groups}

Abani Patra, Univ @ Buffalo
Alan Simpson,  EPCC, The University of Edinburgh
Aleksandra Pawlik, Software Sustainability Institute
Alice Allen, Astrophysics Source Code Library (ASCL)
Andre Luckow, Rutgers
Andy Nutter-Upham, Whitehead Institute
Anshu Dubey  Lawrence Berkeley National Laboratory
Ardita Shkurti University of Nottingham
Benjamin Pharr, University of Mississippi
Berkin Malkoc, Istanbul Technical University
Bryan Marker, The University of Texas at Austin
Carl Boettiger, UCSC/ropensci
Carol Song, Purdue University
Chris Bogart, ISR/CMU
Chris Lenhardt
Cody J Permann, Idaho National Laboratory
Colin C. Venters, University of Huddersfield
Daniel S. Katz, U Chicago \& Argonne
David Bernholdt, Oak Ridge National Laboratory
David Henty,  EPCC, The University of Edinburgh
Dirk Colbry, Michigan State University
Eric Hutton,  University of Colorado
Erin Robinson, Foundation for Earth Science 
Ethan Davis, UCAR Unidata
Ethan White, University of Florida/Utah State University
Frank L\"{o}ffler, Louisiana State University
Frank Seinstra Netherlands eScience Center
Gabrielle Allen, U Illinois
Greg Wilson  Software Carpentry
Hilmar Lapp, National Evolutionary Synthesis Center (NESCent) and Duke University
James Howison, University of Texas
James Shepherd, Rice University
James Spencer, Imperial College London
John W. Cobb
John W. Peterson, Idaho National Laboratory
Jordan Adams, Tulane University
Jory Schossau, Michigan State University
Kaitlin Thaney,  Mozilla Science Lab
Karen Cranston, NESCent
Karthik Ram, , University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
Kurt Glaesemann Pacific northwest national lab
Kyle Marcus, University of Buffalo
Marcus D. Hanwell, Kitware
Mark Schildhauer,  NCEAS, Univ. Calif, Santa Barbara
Marlon Pierce, Indiana University
Matt Jones,  University of California Santa Barbara
Matt Turk, NCSA/UIUC
Mike Rilee - NASA/GSFC, Rilee Systems Technologies - 
Nancy Wilkins-Diehr, SDSC
Neil Chue Hong, Software Sustainability Institute \& University of Edinburgh, N 
Nick Jones, New Zealand eScience Infrastructure, University of Auckland
Nicole Gasparini, Tulane University, New Orleans
Pierre-Yves Aquilanti TOTAL E\&P R\&T USA
Ray Idaszak, RENCI/UNC
Ray Plante, NCSA/University of Illinois Urbana-Champaign
Richard Littauer, MIT/University of Saarland 
Robert H. McDonald - Indiana University - Data to Insight Center/Libraries - 
Robert R Downs, CIESIN, Columbia University
Samin Ishtiaq, Microsoft Research Cambridge, UK
Sarah Harris, University of Leeds
Sol Greenspan  National Science Foundation
Stephen Piccolo,  Brigham Young University, Utah
Steven R. Brandt, Louisiana State University
Suresh Marru, Indiana University 
Sushil Prasad, Georgia State University, Atlanta 
Ted Habermann, The HDF Group
Tom Clune - NASA GSFC - 
Tom Crick, Cardiff Metropolitan University, UK
Tracy Teal Data Carpentry
Wolfgang Bangerth
Yolanda Gil, Information Sciences Institute, University of Southern California

% Names below were in the working groups but were not present in the above list

Ian Kelley 
Jakob Blomer
Justin Shi
Maxime Hughes
Mike Rilee
Nathan Weeks
Rupert Nash
